---
title: "Case Study: Cheese"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Case Study: Cheese}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MolPad)
library(dplyr)
```

# Load Data
In the process of producing cheese, regular washing with a brine solution is an aging practice that can homogenize the microbial communities on the cheese' surface and facilitate intermicrobial interactions. In the following parts, we will analyze a longitudinal data set of three washed-rind cheese communities collected during cheese ripening.

```{r}
data("cheese")
```

# Preprocess
## Data and Annotations
Here we select a 'type' column with `phylum` to describe the characteristic of cheese data. Also, the columns `phylum` and `class` are taken as tags for elemental composition.

```{r}
cheesedata <- cheese |> 
   		 select(ID, A_1:C_5, phylum) |> 
   		 rename(type=phylum) |> 
      		pre_process()
```

```{r}
pathchee <- gAnnotation(annotations,"phylum","class")
```

### After pre-processing, here is what the two datasets that we will put into the dashboard look like:
```{r}
cheesedata[112:115,]
pathchee[112:115,]
```


## Cluster Input
Then we generate clusters from the long dataset above. 
```{r}
cluschee <- gClusters(cheesedata,ncluster = 10,elbow.max=15)
```

## network input
After that, we got the network result from the clusters. We pick top 3 predictors for each feature, and save the network output for future use.
```{r}
networkchee <- gNetwork(cluschee,ntop = 3)
```

View more details of the results with the following function:
```{r,fig.height=9, fig.width=5}
gNetwork_view(networkchee)
```

# Run Dashboard
Declare the annotations, and then run the dashboard.
```{r,eval=FALSE}
gDashboard(cheesedata,
           cluschee,
           pathchee,
           networkchee,
           id_colname = c("GO_ID","KEGG_ID"),
           id_type = c("GO","KEGG"))
```
