---
title: "Cheese"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cheese}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MolPad)
```

# Load Data
In the process of producing cheese, regular washing with a brine solution is an aging practice that can homogenize the microbial communities on the cheese' surface and facilitate intermicrobial interactions. In the following parts, we will analyze a longitudinal data set of three washed-rind cheese communities collected during cheese ripening.

```{r}
annotations <- merge(f12,t12,by="ID")

cheese <- c12

save(cheese,annotations,file="cheese.RData")
```

```{r}
data("cheese")

cheesedata <- cheese %>%
  mutate(annotations["kingdom"]) %>%
  rename(type=kingdom) %>%
  pre_process()

#-----------------------run cheese----------------------
#-------- process cheese12 data--------



chee <- merge(c12,t12[,c("ID","kingdom")],by="ID")
colnames(chee)[12] <- 'type'

chee$type[is.na(chee$type)] <- "Other"
chee[,1:11] <- scale_by_row__(chee[,1:11])

#if the number does not change, then remove the feature
chee <- na.omit(chee)

#----------------------
cluschee <- gClusters(cheesedata,ncluster = 10,elbow.max=15)
networkchee <- gNetwork(cluschee,ntop = 3)

pathchee <- annotations %>%
  rename("taxonomic.scope" = "class") %>%
  rename("Pathway" = "phylum")

#问题：第一个pathway显示不对,估计是gdashboard开头的问题

annotations

gDashboard(cheesedata,cluschee,pathchee,networkchee,dashboardtitle = "Test","KEGG_ID")

#-----

data <- cheese
data$ID <- as.numeric(data$ID)

to_scale <- data[,(unlist(lapply(data, is.numeric)))&(names(data) %in% c("ID","id","Id")==FALSE)]
scaled <- as.data.frame(t(apply(to_scale, 1, scale)))
data[,(unlist(lapply(data, is.numeric)))&(names(data) %in% c("ID","id","Id")==FALSE)] <- scaled
data

scale_by_row__ <- function(data){
  to_scale <- data[,(unlist(lapply(data, is.numeric)))&(names(data) %in% c("ID","id","Id")==FALSE)]
  scaled <- as.data.frame(t(apply(to_scale, 1, scale)))
  data[,(unlist(lapply(data, is.numeric)))&(names(data) %in% c("ID","id","Id")==FALSE)] <- scaled
  data
}

scale_by_row__(data)

data[2,2] = NA

na.omit(data)
data
```

# Preprocess
## data input
We first reshape the datalist into our standard format. The type column is to describe datasets from the input, and if not specified, the type will be auto-filled with "dataset 1", "dataset 2", etc.
```{r}
a <- pre_process(fungal_dlist,typenameList = c("Peptide","Metabolite","Lipid"))
# The following dataset is our standard input:
head(a,3)
```

## cluster input
Then we generate clusters from the long dataset above. The number of clusters can be adjusted according to the elbow method plot in `b[[2]]`, where we picked one close to the inflection point.
```{r}
b <- gClusters(a,ncluster = 15)
#b[[1]] has all the cluster level information, includes: cluster, center, totss, withinss, betweens, size, iter, and ifault.
#b[[2]] is the WSS plot for different number of clusters.
b[[2]]
```
## network input
After that, we got the network result from the clusters. We pick top 5 predictors for each feature, and save the network output for future use.
```{r}
networkres <- gNetwork(b,ntop = 5)
```

Users could also view more details of the results with the following function:
```{r,fig.height=9}
gNetwork_view(networkres)
```

# Run Dashboard
Name the title and declare the annotations, and then run the dashboard.
```{r,eval=FALSE}
gDashboard(a,b,pathway,networkres,
           dashboardtitle = "MolPad Dashboard",
           annotations="ko_term")
```
