---
title: "Data Input: Multi-Omics/Single-Omics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Input: Multi-Omics/Single-Omics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
Our visualization pipeline begins with an optional pre-processing module that offers built-in functions to streamline data preparation. Depending on the nature of your datasets, there are two primary conditions to consider:

# If Your Datasets are Multi-Omics:
In this scenario, we assume that you provide a list of data tables, each collected for a different omics type. For example, you might have datasets for peptides, metabolites, and lipids. We recommend carefully reviewing your data and considering applying quantile normalization and KNN imputation to address issues related to library size and missing data.

To achieve this, simply run the pre_process() function, which will yield the standard input format as demonstrated below.

```{r, echo=FALSE}
# Simulated data with the standard input format 
x <- data.frame("ID"=1:5,"Day_1"=rnorm(5),"Day_2"=rnorm(5),"Day_3"=rnorm(5),"Day_4"=rnorm(5),"Day_5"=rnorm(5),"Day_6"=rnorm(5),"Day_7"=rnorm(5),"Day_8"=rnorm(5),"type"=c(rep("peptide",3),"lipid","metabolite"))
x
```


# If Your Datasets are NOT Multi-Omics:

You can still utilize our dashboard by ensuring that your data inputs are reformatted into the standard longitudinal format. While the datasets may not be multi-omics, you can manually assign the type column with any category label to describe major groups in the data. In our case study, we utilized "Kingdom" as the type label column for the cheese data.

# Choose Your Annotation

In addition to specifying the data type mentioned above, our methods support three levels of information: functional annotation, taxonomy annotation, and feature annotation. These annotations will be matched with ID columns in the annotation data, serving as another crucial input for generating the dashboard. We facilitate automatic feature link generation using KeggID and GOID, for which users should set the corresponding column names beforehand.







