---
title: "Why MolPad?"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Why MolPad?}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MolPad)
library(dplyr)
```


# Why MolPad?

With the increasing multi-omics data and longitudinal designs integrated into microbiome experiments, there is a growing need to present the network, especially with complex variations across biological modalities. Network perspective helps detect the underlying co-occurrence among microbiome samples, allowing for high-level insights into the global structure. Yet when it comes to experimental data that records time series for 100,000 features, the network will collapse into some entangled clumps and therefore unable to read. 

For the aim of network interpretation, MolPad shows improvements in two important aspects:

Capture groups of features that share longitudinal patterns and functional properties within the network. 
Annotate the network under complex experimental datasets, as a way to dig in specific components with notable features. 

This package especially facilitates the exploration of longitudinal molecular co-expression in microbiome experiments using a focus-plus-context and interactive approach, empowering researchers to uncover global patterns and insights in longitudinal microbiomics data. 

Furthermore, MolPad streamlines exploration through interactive features such as taxonomic composition visualization, feature trajectory clustering, and automatic links to online annotation. Unlike existing tools, MolPad stands out for its rich network interactivity and support for contextualization. It is also equipped with a beginner-friendly interface and self-contained data processing functions, making it accessible to users with limited programming experience. 



